---
title: "Amanda Cao"
author: "Amanda Cao"
date: "2024-09-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Education
- Emory University, **2021 - 2025**
  - BS in QSS Informatics and Biology
  - GPA: 3.9

- Palos Verdes Peninsula High School, **2017 - 2021**
  - GPA: 3.98
  
## Employment
- AGC Partners, **June 2024 - July 2024**
  - Technology Investment Banking Summer Analyst
  - Wrote a 40+ page report on restaurant technology, focusing on catering event software solutions; conducted market sizing,identified demand drivers and challenges, and mapped the competitive landscape to uncover growth opportunities

- Bravaldo Capital Advisors, **June 2023 - July 2023**
  - Constructed CIM with the junior team on selling an Atlanta-based firm in the security industry, conducted extensive industry research on the industry landscape, and analyzed recent trends and major players to identify potential growth trajectories
  - Advised a construction company on its sell-side transaction, organized financials and constructed a three-statement model
  
```{r}
options(repos = c(CRAN = "https://cran.rstudio.com/"))
install.packages("renv", type = "binary")
renv::init()
renv::snapshot()
```


```{r}
usethis::use_git()
```

